Hybrid MILP to efficiently and accuratly \\ solve hard DNN verification instances

### 2024-11-26 ICLR25/experiments.tex
exp
polish
fork of appendix. Please use proofsb.tex

We focus on the uncertainty of nodes in the third layers, wrt ReLU nodes in the first and second layer. The bounds for nodes of the first two layers are computed exactly using the full MILP encoding. We report in Table \ref{tab:example1} the average uncertainty of $\MILP_X$ following the choice of the $K$ heaviest neurons for our {\bf Utility} function, compared with a random choice, both for nodes exclusively from the previous Layer 2 or from both Layers 1 and 2. We compared with choosing based on strength$(n) = (\UB(n)-\LB(n))\cdot |W_{nz}|$ \cite{DivideAndSlide}, which is limited to the previous Layer 2.

\begin{table}[h!]	
	\centering
	\begin{tabular}{|c||c|c|c||c|c|}
		\hline
			&\multicolumn{3}{c||}{$X \subseteq$ Layer 2, max $=61$}&\multicolumn{2}{c|}{$X \subseteq$ Layers 1\&2, max $=116$}\\\cline{2-6}
		\text{$|X|$}  & \text{Random} & \cite{ DivideAndSlide} & \bf Utility& \text{Random} &\bf Utility\\ \hline
		\hline
		0  (LP) &   1.761  &1.761& 1.761 & 1.761  & 1.761\\ \hline \hline
		5  &   1.729&1.704 & 1.603&  1.729&  \bf 1.532 \\ \hline
		10  &  1.701 &  1.651 &1.517& 1.696 & \bf  1.371\\ \hline
		15  & 1.671 &  1.599 &1.466&  1.653& \bf  1.247\\ \hline
		20  &  1.635 & 1.557&1.438 & 1.619 & \bf  1.145\\ \hline
		25  &  1.601 & 1.519 &1.427&  1.586 & \bf 1.061\\ \hline
		30  & 1.574 & 1.489 &1.425& 1.546 & \bf  0.989 \\ \hline
		35  &  1.542 & 1.465&1.424 & 1.502 & \bf 0.934 \\ \hline
		40  & 1.512 & 1.447 &1.424& 1.469 & \bf 0.921 \\ \hline \hline
		max & 1.424  &1.424& 1.424 & 0.895 & 0.895   \\ \hline
	\end{tabular}
	\caption{Average uncertainty of $\MILP_X$ for nodes of the third layer, for $X$ with $K$ ReLU nodes of the (1st and) 2nd layer, chosen by our {\bf Utility} function vs \cite{ DivideAndSlide} vs random choice.}
	\label{tab:example1}
	%\vspace{-0.6cm}
\end{table}

@@

>>>>

We focus on the uncertainty of nodes in the third layers, wrt ReLU nodes in the first and second layer. The bounds for nodes of the first two layers are computed exactly using the full MILP encoding. We report in Figure \ref{fig_table3} the average uncertainty of $\MILP_X$ following the choice of the $K$ heaviest neurons for our {\bf Utility} function, compared with a random choice, both for nodes exclusively from the previous Layer 2 or from both Layers 1 and 2. We compared with choosing based on strength$(n) = (\UB(n)-\LB(n))\cdot |W_{nz}|$ \cite{DivideAndSlide}, opening nodes in Layer 2 only.

\iffalse
\begin{table}[h!]	
	\centering
	\begin{tabular}{|c||c|c|c||c|c|c|}
		\hline
			&\multicolumn{3}{c||}{$X \subseteq$ Layer 2, max $=55$}&\multicolumn{3}{c|}{$X \subseteq$ Layers 1\&2, max $=116$}\\\cline{2-7}
		\text{$|X|$}  & \text{Random} & Huang & \bf Utility& \text{Random} &BSR &\bf Utility\\ \hline
		\hline
		0  (LP) &   1.761  &1.761& 1.761 & 1.761  &  1.761& 1.761\\ \hline \hline
		5  &   1.729&1.704 & 1.603&  1.729& 1.7138 &  \bf 1.532 \\ \hline
		10  &  1.701 &  1.651 &1.517& 1.696 & 1.6775& \bf  1.371\\ \hline
		15  & 1.671 &  1.599 &1.466&  1.653& 1.6392& \bf  1.247\\ \hline
		20  &  1.635 & 1.557&1.438 & 1.619 &1.5938 & \bf  1.145\\ \hline
		25  &  1.601 & 1.519 &1.427&  1.586 &1.5534 & \bf 1.061\\ \hline
		30  & 1.574 & 1.489 &1.425& 1.546 & 1.5166& \bf  0.989 \\ \hline
		35  &  1.542 & 1.465&1.424 & 1.502 & 1.4788 & \bf 0.934 \\ \hline
		40  & 1.512 & 1.447 &1.424& 1.469 & 1.4395& \bf 0.921 \\ \hline \hline
		max & 1.424  &1.424& 1.424 & 0.895 & 0.895 & 0.895   \\ \hline
	\end{tabular}
	\caption{Average uncertainty of $\MILP_X$ for nodes of the third layer, for $X$ with $K$ ReLU nodes of the (1st and) 2nd layer, chosen by our {\bf Utility} function vs \cite{ DivideAndSlide} vs random choice.}
	\label{tab:example1}
	%\vspace{-0.6cm}
\end{table}
\fi

@@

\begin{figure}[h!]
	\centering
	\vspace*{-0.3cm}
	\includegraphics[height=7.5cm]{Plot for table 3}.
	\vspace*{-0.4cm}
	\caption{Average uncertainty of $\MILP_X$ for nodes of the third layer, for $X$ with $K$ ReLU nodes of the (1st and) 2nd layer, chosen by our {\bf Utility} function vs \cite{ DivideAndSlide} vs random choice.}
	\label{fig_table3}
\end{figure}
